Calendar-based graphics for visualising people's daily schedules

### 2017-06-07 main.Rmd
update monashwp template

---
title: "Calendar-based graphics for visualising people's daily schedules"
author: "Earo Wang, Di Cook, Rob J Hyndman"
fontsize: 11pt
papersize: a4
fontfamily: mathpazo
bibliography: references.bib
biblio-style: authoryear-comp
subparagraph: true
toc: false
output: 
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    number_sections: yes
    citation_package: biblatex
---

@@

\begin{abstract}
 A brief summary of our ideas
\end{abstract}

\begin{keywords}
  blah, blah
\end{keywords}

\newpage

>>>>

---
title: "Calendar-based graphics for visualising people's daily schedules"
author:
  - familyname: Wang
    othernames: Earo
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : earo.wang@monash.edu
    correspondingauthor: true
  - familyname: Cook
    othernames: Di
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : dicook@monash.edu
  - familyname: Hyndman
    othernames: Rob
    address: Department of Econometrics and Business Statistics, \newline Monash University, VIC 3800 \newline Australia.
    email : rob.hyndman@monash.edu
fontsize: 11pt
papersize: a4
fontfamily: mathpazo
blind: false
cover: true
wpnumber: no/yr
jelcodes: C10,C14,C22
bibliography: references.bib
biblio-style: authoryear-comp
abstract: "A brief summary of our ideas"
keywords: "blah, blah"
subparagraph: true
toc: false
output: 
  bookdown::pdf_document2:
    template: monashwp.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    number_sections: yes
    citation_package: biblatex
---

@@
